Predicting The Outcome T1 and Gen G Games Based on Leads

### 2024-04-19 paper/paper.qmd
finalized paper document

---
title: "Election Preferences in 2022 based on Gender and Education"

author: 
  - Rahul Gopeesingh
thanks: "Code and data are available at:https://github.com/Rahul-Uoft/election.git"
date: today
date-format: long
abstract: "There are many factors that can influence someone's voting preference. Two of which that seem very relevant are a person's gender as well as their education level. This paper uses a logistic regression to investigate the relattionship between these factors and a person's political preference. We found that both females and highly educated people are significantly more likely to vote for Biden than for Trump"
format: pdf
number-sections: true
bibliography: references.bib
toc: TRUE
---

@@

library(tidyverse)

library(boot)
library(broom.mixed)
library(collapse)
library(dataverse)
library(gutenbergr)
library(janitor)
library(knitr)
library(marginaleffects)
library(modelsummary)
library(rstanarm)
library(tidybayes)
library(tidyverse)
library(arrow)
library(ggplot2)
```

@@

This paper seeks to shed light on this historic rivalry by analyzing how good the players are at using their leads to close out games. The two types of leads that we will look at will be a high gold income as well as a straight out experience lead against their 'lane opponent'(more details are in the discussion)

@@

The remainder of this paper is structured as follows. @sec-data discusses the data, how it was collected and the purpose in which we use this data. It also gives a brief analysis of the data. @sec-mod walks through the logistic regression model used and the justification for using this logistic regression. @sec-res shows the results and an intepretation of what they mean. Finally, @sec-dis discusses the potential reasons behind these results and their implications.

@@

>>>>

---
title: "Predicting The Outcome T1 and Gen G Games Based on Leads"

author: 
  - Rahul Gopeesingh
thanks: "Code and data are available at:https://github.com/Rahul-Uoft/Match-Prediciton.git"
date: today
date-format: long
abstract: "T1 and Gen G are two of the best League of Legends teams in the world with a longstanding rivalry. In a game of league of legends, the early focus of the game is not the primary objective, but rather, gain advantages so that it is easier to achieve the primary objective. Some teams are really good at throwing away the advantages they did so well to accrue. This paper investigates how good T1 and Gen G are at converting their leads into a win. The model predicts that Gen G is better at playing with leads, and are more likely to convert to a win, but are much worse playing without them. This information can be used by coaching staff to gain knowledge about the players as well as other teams to devise strategies to play against them."
format: pdf
number-sections: true
bibliography: references.bib
toc: TRUE
---

@@

library(tidyverse)
library(modelsummary)
library(rstanarm)
library(tidybayes)
library(tidyverse)
library(arrow)
library(ggplot2)
```

@@

This paper investigates this historic rivalry by analyzing how good the players are at using their leads to close out games. The two types of leads that we will look at will be a high gold income as well as a straight out experience lead against their 'lane opponent'(more details are in the discussion) We are attempting to estimate how much more likely a team is to winning a game based on how much minions they killed in the first 10 minutes or the highest level lead they had against their opponent.

It was found that Gen G players are 10 times as likely to win a game in which they are 2 levels up on their opponent whereas T1 players are only 4 times as likely to win such a game. This indicates that Gen G is much better at closing out a game with a lead than T1. Conversely, T1 players have a lot better chances of winning a game in which they do not have an advantage. Overall there aren't many differences between the teams in a general sense, but these two stood out as significant as they shed light on stylistic differences. These can be used by other teams to devise strategies when playing against either Gen G or T1 as well as by the T1 and Gen G staff to improve on their weaknesses.

@@

The remainder of this paper is structured as follows. @sec-data discusses the data, how it was collected and the purpose in which we use this data. It also gives a brief analysis of the data. @sec-mod walks through the logistic regression model used and the justification for using this logistic regression. @sec-res shows the results and an interpretation of what they mean. Finally, @sec-dis discusses the potential reasons behind these results and their implications.

@@

There are many ways in which the findings of this paper can be used. For instance, if another team notices that Gen G is a lot more likely to lose if they don't have high cs at 10 minutes then they can alter their playstyle in a way that maximizes their chances of keeping Gen G at a low cs level in the early game. This tactic won't work against T1 as they are completely fine not getting a lot of cs in the early game. Coaches of both of these teams can also use this by trying to sharpen their strengths or cover their weaknesses. For instance, T1 coaches can try to help the players get better at closing out games with level leads.
